%!TEX root = dbproposal.tex

In this section of the proposal, we outline our efforts to analyze,
implement, and compare the most promising schemes from the previous two
sections. These efforts will be \emph{concurrent} and \emph{ongoing}
with the theoretical developments. A main goal of our approach is to create cryptographic search systems that will be deployable in the future.  Thus, it is critical to understand
the practical implications of different approaches.

%The main goals of this thrust of our work is to put our schemes in
In particular, we would like to put our schemes in
context of existing approaches and provide clear comparisons for
practitioners and researchers alike.
The work of this section will also feature the most prominent engagement with
student researchers, not only graduate but also undergraduate students, at our
respective institutions.

\subsection{Leakage analysis}

All of the schemes we have proposed make some compromise of leakage for
performance. Unfortunately, many prior works either focus primarily on security
proofs and (sometimes novel) security definitions, or make heuristic
arguments for security. It is rarely clear how to compare the leaked information.  This means it is not
straightforward, for example, to decide what is ``more secure'' between
different approaches.  This difficulty in comparing is not only a semantic gap. Sometimes leaked information is damaging for a particular use case and innocuous for another.  This ambiguity suggests the need for standard and comprehensive benchmarks.

One of PIs made progress towards fair comparisons in a recent
Systemization of Knowledge~\cite{SP:FVYSHG17}. We will continue in this vein and use existing
metrics whenever possible to place our work in a fair context within the
state of the art.  Two main components of this fair comparison are 1) the use of  consistent naming for leakage and 2) maintaining a partially-ordering of schemes' leakage.

For this analysis to be meaningful, cryptographic designers must be cognizant of
recent attacks on PPE and related schemes such as
\cite{CCS:CGPR15,CCS:KKNO16}. These attacks often depend crucially on
the datasets used and the assumed prior knowledge, and we will use the same (or equivalent) attacks
against our schemes to provide a meaningful comparison.

Much of the work of this proposal is in extending existing
non-interactive and interactive schemes to the multi-dimensional setting
via some support of distance queries. Some existing metrics can apply
directly in this setting, for example the notion of \emph{incomparable
pairs} introduced in \cite{CCS:RACY16}. Other notions related to
closeness, i.e., \emph{pairwise distance}, also make sense in a
Euclidean space. Rather than develop entirely new definitions, when
possible we will use existing metrics to quantify the security
improvements our schemes provide.

\subsection{Implementation and experimental analysis}

\emph{Throughout all phases of the project}, the most promising of our
schemes will be implemented and tested on realistic scenarios.
Indeed, we plan to include
experimental components in many of our published artifacts, with
links to the open source implementations developed.

Compatibility with existing database software is a key priority of
our approach.  We will seek to incorporate our schemes within existing
open-source projects such as the SSE library Clusion
({\small \url{https://github.com/encryptedsystems/Clusion}}) and
the cloud-based graph database software
Apache Rya ({\small \url{https://rya.apache.org/}}).

In order to evaluate the real-world performance of our schemes, we will
be careful to use realistic and relevant datasets and queries. Tools
such as the automatic test-suite generator that one of the co-PIs co-developed
in the IARPA SPAR project \cite{HH14,varia2015automated} will be used to
generate repeatable and realistic experiments.  As necessary, we will extend
these tools to support proximity databases.  We expect to extend both data and
query generation.  As possible, these changes will be fed back into the
existing open-source projects.

Our experimental evaluations will also cover the \emph{security} of our
schemes. The approaches we propose all
entail some limited information leakage.
We will use empirical tools to highlight the practical
implications of this limited leakage, including leakage under known
attacks. For example, in \cite{CCS:RACY16}, two of the co-PIs not only
evaluated the number of incomparable ciphertext pairs in theory, but
also tested this leakage on a publicly-available salary database.  Working with the community, we will identify a small set of datasets that highlight the different leakage profiles in the literature.  We expect these datasets can be used to effectively communicate the tradeoffs between different schemes.
