\documentclass[11pt]{article}

\usepackage{fullpage,varwidth,url}
\usepackage{amssymb}
\usepackage{amsmath,amsthm}
\usepackage{relsize}
\usepackage{color}
\usepackage{enumitem}

\def\BI{\begin{itemize}}
\def\EI{\end{itemize}}

\begin{document}

\begin{center}
{\LARGE Biographical Sketch: Seung Geol Choi}
\end{center}


\begin{enumerate}[label=\textbf{(\alph*)}]

\item \textbf{Professional Preparation}
\BI
\item {\it Undergraduate Institution} \\
Seoul National University, Seoul, South Korea\\ 
$~~~~~$ B. Sc., Computer Engineering, 1999. 

\item {\it Graduate Institutions} \\
Seoul National University, Seoul, South Korea\\ 
$~~~~~$ M. Sc., Electrical Engineering and Computer Science, 2005. 

Columbia University, New York, NY, U.S.A\\
$~~~~~$ M. Phil., Computer Science, 2009. \\
$~~~~~$ Ph.D., Computer Science, 2010. 

\item {\it Postdoctoral Institutions} \\
University of Maryland, College Park, MD, U.S.A \\ 
$~~~~~$ Postdoctoral Researcher on Efficient Secure Computation, 2010 - 2012.

Columbia University, New York, NY, U.S.A\\
$~~~~~$ Postdoctoral Researcher on Private Database Systems. 2012 - 2013. 
\EI


\item \textbf{Appointments}
\BI
\item United States Naval Academy, Computer Science Department \\
$~~~~~$ Assistant Professor, September 2013 - Present.

\item Columbia University, Computer Science Department \\ 
$~~~~~$ Adjunct Assistant Professor, January 2012 - May 2013. \\
\EI


\item {\bf Publications}
\begin{enumerate}[label=(\roman*)]
\item Closely related to proposed project
\begin{enumerate}[label=\arabic*.]

\item 
Vasilis Pappas, Fernando Krell, Binh Vo, Vladimir Kolesnikov, Tal Malkin, Seung
Geol Choi, Wesley George, Angelos Keromytis, Steven Bellovin.  ``Blind Seer: A
    Scalable Private DBMS".  In Proceedings of IEEE Symposium on Security and 
    Privacy (Oakland), pages 178-197. 2014. 

\item
Daniel S. Roche, Daniel Apon, Seung Geol Choi, and Arkady Yerukhimovich. POPE:
Partial order preserving encoding. In ACM CCS 16, pages 1131-1142.  2016.

\item 
Daniel S. Roche, Adam J. Aviv, and Seung Geol Choi. A practical oblivious map
data structure with secure deletion and history independence. In 2016
IEEE Symposium on Security and Privacy (Oakland), pages 178-197. 2016.


\item 
Daniel S. Roche, Adam J. Aviv, Seung Geol Choi, and Travis Mayberry.
Deterministic, stash-free write-only oram. In ACM CCS 17, pages 507-521. 2017.


\item 
Seung Geol Choi, Jonathan Katz, Alex J. Malozemoff, and Vassilis Zikas.
Efficient three-party computation from cut-and-choose. In CRYPTO 2014,
Part II, volume 8617 of LNCS, pages 513-530. Springer, Heidelberg, August
2014.

\end{enumerate}

\item Other significant publications

\begin{enumerate}[label=\arabic*.]
\item
Adam J. Aviv, Seung Geol Choi, Travis Mayberry, and Daniel S. Roche.
Oblivisync: Practical oblivious file backup and synchronization. In NDSS
2017. The Internet Society, 2017.

\item
Kwangsu Lee, Seung Geol Choi, Dong Hoon Lee, Jong Hwan Park, and Moti Yung.
    ``Self-Updatable Encryption: Time Constrained Access Control with Hidden
    Attributes and Better Efficiency". In Proceedings of  Advances in
    Cryptology (ASIACRYPT). 2013.


\item
Seung Geol Choi, Kyung-Wook Hwang, Jonathan Katz, Tal Malkin, and Dan
Rubenstein.  
``Secure Multi-Party Computation of Boolean Circuits with
Applications to Privacy in On-Line Marketplaces".
In CT-RSA. 2012. 

\item 
Seung Geol Choi, Aggelos Kiayias and Tal Malkin.
``BiTR: Built-in Tamper Resilience." 
In ASIACRYPT. 2011.


\item
Seung Geol Choi, Dana Dachman-Soled, Tal Malkin, and Hoeteck Wee. 
``Black-box Construction of a Non-Malleable Encryption Scheme from Any Semantically Secure One."
In TCC. 2008. 
\end{enumerate}
\end{enumerate}

\item {\bf Synergistic Activities}

\begin{enumerate}[label=\arabic*.]
 \item Teach classes on Introudction to CS (2017), Theory of Computing
    (2013-2016), Cyber Security Foundations (2013-2017), and Security
    Fundamental Principles (2014-2017).
\item Program Committee Member at
  WAHC 2017 (Workshop on Encrypted Computing and Applied Homomorphic
   Cryptography), ACNS 2015, ProveSec 2014, CT-RSA 2013, ESORICS 2012, and
  INSCRYPT 2011.   
\item PhD Dissertation Committee Member: \\
    Jesus Diaz Vico (Computer Science, UAM, Spain) May 2015.
\item Master Thesis, committee member: \\
Vaishali Narkhede (Computer Science, UMBC): April 2016
\end{enumerate}

\item {\bf Collaborators \& Other Affiliations}
\BI

\item Collaborators:
	  Adam Aviv (USNA);
    Elli Androulaki (IBM Zurich);
    Steven Bellovin (Columbia University); 
    Carlos Cid (Royal Holloway,University of London);
    Dana Dachman-Soled (University of Maryland, College Park);
    Tim Finin (University of Maryland, Baltimore County); 
    Angelos Keromytis (Columbia University);
    Aggelos Kiayias (National and Kapodistrian University of Athens);
    Vladimir Kolesnikov (Bell Labs);
    Ranjit Kumaresan (MIT);
    Kwangsu Lee (Korea University, Korea);
    Dong Hoon Lee (Korea University, Korea);
    Javier Lopez (University of Malaga, Spain);
	  Travis Mayberry (USNA);
    Karuna Josh (University of Maryland, Baltimore County);
    Dan Rubenstein (Columbia University);
    Dominique Schr{\"o}der (Saarland University, Germany);
    Hoeteck Wee (\'Ecole Normale Sup\'erieure, France);
    Arkaday Yerukhimovich (MIT Lincoln Lab);
    Vassilis Zikas (ETH Zurich); 
    Hong-Sheng Zhou (Virginia Common Wealth University). 

\item Graduate Advisers: Kunsoo Park (Seoul National
    University); Tal Malkin (Columbia University); Moti
    Yung (Columbia University and Google Inc.).
\item Postdoctoral Advisers:  Jonathan Katz (University of
    Maryland, College Park); Tal Malkin (Columbia University);
\EI
\end{enumerate}

\end{document}
