%\documentclass{llncs}

%\documentclass[11pt]{article}

\documentclass[11pt]{article}
\pagestyle{plain}
%\pagenumbering{arabic}
%\pagestyle{empty}

\usepackage{url}

\setlength\pdfpageheight{\paperheight}
\setlength\pdfpagewidth{\paperwidth}

\parindent=0cm
\setlength{\textwidth}{6.8in}
\setlength{\textheight}{9.2in}
\setlength{\oddsidemargin}{-.1in}
\setlength{\evensidemargin}{-0.1in}
\setlength{\topmargin}{-.5in}

\begin{document}

\newcommand{\etalchar}[1]{$^{#1}$}

$\mbox{ }$


\begin{center}
{\Large \bf Facilities and Equipment}
\end{center}

%\vspace{0.2in}

%\parbox[t]{4in}{
%MIT Computer Science and Artificial Intelligence Laboratory \\
%32 Vassar Street \\
%Cambridge, MA 02139 \\
%Tel: (617) 715-4617 \\
%Email: okhan@csail.mit.edu\\
%}
%\parbox[t]{2.2in}{
% ~
%}


The co-PI, Benjamin Fuller primarily in the department of Computer Science and Engineering at the University of Connecticut in the School of Engineering.   There are design, implementation, and evaluation pieces to this proposal.  The design and implementation pieces do not require the use of laboratories or any other special facilities beyond the usual workplace environment. These tasks do require the use of a computer in order to develop computer programs that implement our designs. 

More critically, the evaluation piece of the project requires more extensive computing resources in order to test our applications. Our plan is utilize University of Connecticut's High Performance Computing cluster which is described below.

\noindent
\section*{Facilities and Equipment at the School of Engineering}

The School of Engineering and Booth Engineering Center for Advanced Technology (BECAT) hosts a HPC cluster. This cluster has the following capabilities:

\begin{itemize}
\item A total of 6.328 CPU cores all with Intel Xeon x64 processors.
\item 33TB is total RAM between machines
\item 1PB of parallel storage
\item 20Gbps Ethernet to campus
\end{itemize}

More information about UConn's HPC capability is available at \url{hpc.uconn.edu}.  UConn's HPC resources are made available to all faculty (and have been used by Dr. Fuller).  In addition, it is possible for faculty to purchase priority on nodes but that is not expected for this project (and is not budgeted).

\noindent

\end{document}
