%!TEX root = dbproposal.tex

\section{Introduction}

The importance of collecting and storing data is universal, with use
cases in governmental~\cite{Powers2014},
commercial~\cite{Linoff:2002:MWT:560274,insightdata}, and personal
sectors~\cite{Mons2011}.
Storing and querying large datasets has tremendous value in improving
decision making, but this growth in size and complexity is increasingly
resulting in organizations relying on external cloud providers for their
data needs.

This outsourced storage represents a natural attack target.  Attacks occur against both government \cite{CyberAttacksOPM} and commercial~\cite{CyberAttacks,gressin2017equifax} datasets.
One natural response to this risk is to encrypt data before outsourcing. 
%
However, employing encryption comes at the cost of disabling the cloud server
from {\em quickly processing the data and answering
complex queries from the client}. 
%
Ideally, we could use more sophisticated cryptographic techniques to {\em create databases
capable of efficiently answering a client's queries without revealing
information to the cloud server}.  

%Secure outsourced databases use advanced cryptography to achieve this goal.  This field encompasses a variety of cryptographic techniques, including property-preserving encryption or PPE~\cite{EC:PanRou12}, searchable symmetric encryption or SSE~\cite{CCS:CGKO06}, private information retrieval by keyword~\cite{EPRINT:ChoGilNao98}, and public-key encryption with keyword search~\cite{EC:BDOP04}.  

Numerous advanced cryptographic techniques have been proposed to achieve
this goal \cite{EC:PanRou12,CCS:CGKO06,EPRINT:ChoGilNao98,EC:BDOP04}.
This research has largely split into two research threads: 
property-preserving encryption (PPE) which
emphasizes background compatibility and use of legacy database
management systems, and searchable secure encryption (SSE) which emphases security.

PPE creates
symmetric encryption techniques
compatible with an unprotected database. Examples include deterministic
encryption~\cite{C:BelBolONe07}, which can answer equality queries, and
order-preserving encryption~\cite{C:BolCheONe11,EC:BCLO09},
which can answer range queries. Academic teams, start-up companies (including Bitglass, Ciphercloud, Crypteron, PreVeil, Skyhigh, ZeroDB) and Fortune
500 companies (including Microsoft's SQL Server 2016 and Azure and Google's Encrypted BigQuery)  offer variants of property-preserving encryption.
%Recent attacks against these schemes indicate even ideal property-preserving
%encryption can't be secure for many applications.

By contrast, SSE schemes can be viewed as starting from secure multi-party
computation and
optimizing solutions for common database tasks (both \cite{SP:FVKKKM15} and \cite{RSA:IKLO16} explicitly use multi-party computation for sensitive subcomputations). This approach requires redesign
of database indexing mechanisms and achieves better security at the cost of decreased efficiency and backward compatibility. 

These systems have been implemented at moderate scale.  Both property-preserving solutions~\cite{CACM:PRZB12,EPRINT:PodBoePop16} and searchable encryption~\cite{SP:PKVKMC14,SP:FVKKKM15,C:CJJKRS13,CCS:JJKRS13,NDSS:CJJJKR14,ESORICS:FJKNRS15,RSA:IKLO16} solutions have been tested on datasets with billions of records.

%
%  Folks--we need to be careful here.  DBMS functions are much broader than search; there's transformation and presentation, access control, backup, recovery management, etc., and we're talking about none of that here.


\subsection{Use Cases}
Emerging databases include large scale graph databases, analytic databases, and
biometric databases. 
\begin{enumerate}
\item Many data sets are naturally interpreted as large sparse graphs.  Examples include social networks such as Facebook and Twitter and communities such as organizational communication, academic co-authorship, and the co-stardom network.  This type of network is also used to perform Internet scale analysis.  Common graph algorithms include computing triangles (sets of nodes $\{a,b,c\}$ where all pairs are close according to a metric), shortest path algorithms, network diameter, and degree distribution.
\item  Increasingly, databases are not asked to return subsets of data
but rather derive statistics and analytics about the stored data.
Machine-learning-as-a-service has emerged as a business model for large
and small companies~\cite{mlservice}.  Many machine learning algorithms
depend on computing distance between points. For example, linear regression finds the
line that minimizes the sum of distances between the line and data
points.  Similarly, the first principal component minimizes the sum of
distances between the selected line and the
dataset~\cite{wold1987principal}.
% The remaining principal components
% are defined similarly (they must also be orthogonal to previously
% defined components).
\item The FBI has long held a fingerprint database with hundreds of millions of records~\cite{brislawn1996fbi} for identifying criminals.  Increasingly, countries are using biometrics as an identifier for citizens, linking biometrics with unique identifiers.  The Aadhaar system in India links biometrics with a unique 12 digit number with over 1 billion numbers issued~\cite{daugman2014600}.  Increasingly, passports are biometric enabled~\cite{stanton2008icao}.  As these databases move to indexing all citizens, privacy concerns abound.
These databases compare the distance between a target point $a$ and the
set of stored points $b_i$, returning all points within some defined
threshold distance from the target.
\end{enumerate}

\noindent
These databases share a fundamental operation: {\em
computing distance/proximity of tuples of points}. 

\subsection{Inadequacy of Prior Work}

In 2000, Song, Wagner, and Perrig provided the first scheme with
communication proportional to the description of the query and the
server performing (roughly) a linear scan of the encrypted
database~\cite{SP:SonWagPer00}.  There has been tremendous work since
2000: both PPE and SSE approaches handle much of SQL and NoSQL queries
and scale to datasets of billions of records.
Though there has been some work on computing shortest paths
\cite{CCS:MKNK15}, in general neither PPE nor SSE
is capable of handling geometric data that is prominent in the
applications discussed above. 
Furthermore, each approach also
has a second weakness:
\begin{enumerate}
\item PPE has been subject to a number of leakage-abuse attacks that show that order-preserving encryption (and sometimes deterministic encryption) is not safe in most cases~\cite{CCS:NavKamWri15,CCS:CGPR15,CCS:KKNO16,CCS:PouWri16,CCS:GMNRS16,EPRINT:GSBNR16,EPRINT:ZhaKatPap16}.  
Nonetheless, industry has primarily adopted this approach.
\item SSE solutions are more limited in functionality and efficiency than PPE based solutions.  The fastest SSE based solutions report overhead of 300\%~\cite{C:CJJKRS13,CCS:JJKRS13,NDSS:CJJJKR14,ESORICS:FJKNRS15} while PPE based solutions report overhead of 30\%~\cite{CACM:PRZB12}.  We are only aware of a single SSE solution that can handle JOIN statements~\cite{EPRINT:KamMoa16}.  As of this writing, the information  leaked by this scheme is not clear.  These solutions replace the entire database software stack with a custom ``cryptographic'' database.  We posit that the lack of backward compatibility and administrative drawbacks hurt industry adoption.  
\end{enumerate}

The emergence of PPE systems indicates the approach has benefits beyond efficiency.  These benefits include backward compatibility, use of legacy software, and improved transparency.
The proposed research will
consider proximity queries as a case study to understand the following
question.  \begin{quote}\emph{Is it possible to securely outsource
modern databases while using a traditional database software stack?
What is the minimum amount that an unprotected database must be modified
to achieve security?}\end{quote}


\paragraph{Out of scope.} We do not address approaches based on
fully-homomorphic encryption~\cite{STOC:Gentry09} or functional
encryption~\cite{FOCS:GGHRSW13}, which are still too slow to be
practical for the data sets we are considering.
In addition, we do not
consider improvements to private information
retrieval~\cite{FOCS:CGKS95} or oblivious
RAM~\cite{STOC:Goldreich87,goldreich1996software} to be in scope for
this proposal, though we may make use of these constructions within our
schemes.
We will also not consider developing new leakage inference attacks.
However, the PIs are well aware of (and have contributed to) to these attacks on
secure databases, and they motivate the solutions we are
proposing.

Lastly, secure enclaves such as Intel SGX offer a promising hardware approach that is being used to isolate programs and provide security~\cite{EPRINT:CosDev16}.  SGX can be used to simulate cryptographic primitives~\cite{EPRINT:SasGorFle17,EPRINT:FVBG16}.  We believe that SGX can be used to upgrade the security of secure databases from honest-but-curious to malicious.  However, we leave combining our techniques with secure hardware to future work.


\subsection{Proposed Work}
The goal of this proposal is to create secure outsourced databases that
will be adopted and used by industry.  Towards achieving this goal we
recognize two lessons from the past: (1) PPE must be carefully analyzed
to understand security and (2) there are tremendous benefits of
maintaining backwards compatibility with existing database systems.
Together, these lessons tell us that some modification of database
systems may be necessary but these modifications should be judicious.
This will be our guiding principle thorough this project.  Our goal is to create a third approach to secure outsourced databases: 
\begin{quote}\emph{Cryptographic operations are restricted to only
database operators (used to create index structures).  These
cryptographic operators can call interactive protocols but do not
require replacing the unprotected database. }
\end{quote}

\noindent
The proposed research will
consider proximity queries as a case study and give constructions supporting
these queries.  The research will be split into three components:
\begin{description}
\item[\Cref{sec:ppe}.] To show the promise of this approach, we
will first consider whether property-preserving encryption can be used
to answer proximity queries.  We expect that the strength and utility of
\emph{distance-preserving encryption} will depend on the definition of
security, in particular questions such as: (1) should distance be precisely preserved? 
(2) is distance-revealing encryption sufficient? and (3) what is the distance
metric? Building on the research of the PI on order-preserving
encryption~\cite{EC:BCLO09,C:BolCheONe11}, this component will consist
of the following tasks:
\begin{enumerate}
\setlength\itemsep{0em}
\item Analysis of security provided by distance-preserving and distance-comparison preserving encryption for common metrics
\item Design of distance-revealing encryption
\item Design of approximate distance-revealing encryption
\end{enumerate}

\item[\Cref{sec:interactive}.] When the security provided by
distance-revealing encryption appears inadequate for an application, we
will change the model to allow operators to call interactive protocols.
We will show what functionality can be built using \emph{interactive
operators}, drawing on partial order-preserving encryption (POPE), recent work of the
co-PIs~\cite{SP:PKVKMC14,CCS:RACY16}.  Considering interactivity is very natural in a client-server setting. This component will consist of
the following tasks:
\begin{enumerate}
\setlength\itemsep{0em}
\item Developing \emph{Partial Distance-Preserving Encryption} for Euclidean and distance proximity  queries
\item Adding forward security to POPE via
  re-insertions and random shuffling
\item Enabling multidimensional queries in BlindSeer and removing the need for
  additive homomorphic encryption and secure two-party computation in the outsourced storage
  setting 
\item Judiciously incorporating oblivious RAM (ORAM) to reduce leakage
\item Developing a new hybrid approach that uses approximate
  distance-revealing encryption and interactive protocols to obtain
  better performance and backwards compatibility
\end{enumerate}

\item[\Cref{sec:analysis}.] Throughout the project, we will implement
and analyze our most promising schemes and place them in a fair context
with prior and ongoing work by others. The goal will be to give
practitioners as well as researchers a clear and \emph{consistent}
picture of the tradeoffs between security, performance, and backwards
compatibility.
We will use the UConn HPC Cluster to evaluate our
implementations on realistic-size databases (\url{https://hpc.uconn.edu}).
We expect this evaluation
to use and extend the database and query generator created as part of
the IARPA SPAR project~\cite{varia2015automated}. The co-PI oversaw development of the most recent version of these tools. Specifically, our
tasks are:
\begin{enumerate}
\setlength\itemsep{0em}
\item Analyzing and developing metrics for the leakage of
information or access patterns inherent in our new PPE and interactive
schemes
\item Developing and providing open-source access to the new tools that
we develop
\item Examining the performance of our approaches on realistic and
repeatable experiments, using industrially-relevant datasets and query
benchmarks
\end{enumerate}
\end{description}

\subsection{Intellectual Merits and Broader Impacts}
\paragraph{Intellectual merits.}  
Encrypted databases and searchable encryption have rich histories rooted in the
design of oblivious random access machines.  The field has been the focus of multiple large scale projects including IARPA's APP and SPAR~\cite{spar_baa}.  The field is quite diverse bringing together cryptographers, system researchers, and database experts.  Furthermore, there is clear demand in industry for solutions.  Data breaches are becoming nearly daily events.  However, recent
leakage inference attacks have taught us that just because something is called encrypted does not make it secure.  This problem requires careful design that balances functionality, efficiency, and security needs.  The rapid deployment of property-preserving
techniques has reinforced the importance of simplicity, efficiency and backward
compatibility.  These two developments inform the core of our approach: using
interactivity to strengthen property-preserving encryption.

\paragraph{Broader impacts.}
The confidentiality of data is a core societal tenant.  Deployed encrypted
databases provide little security and may even hurt by providing a false sense
of security.  There is a tremendous need for research in this area to
understand the tradeoffs between security, functionality, and efficiency.

The PIs are committed to broad dissemination of research material.  The PIs
have participated in large scale evaluation of searchable encryption, working
on both constructions and attacks. The PIs have a track record of
releasing the source code implementations of their work (including
previous work on searchable encryption) and contributing
to open-source projects.
The protocols and other products of this proposal will be released
publicly as open-source implementations.

Lastly, all PIs are
dedicated to engaging with undergraduates. Two co-PIs being at an undergraduate
only institution, the US Naval Academy, where co-PI Roche was recently
recognized with the institution-wide Apgar Award for Teaching. PI O'Neill has
previously been awarded an REU and used it to  work with a female undergraduate
student. Co-PI Fuller supervises the cyber-security club at the University of
Connecticut and supports their efforts to understand and research computer
security.  This club allows students with varying educational preparation to
engage outside of the classroom and learn the impact of computer science and
security. 



