\documentclass[letterpaper,10pt]{article}
\usepackage[margin=1.5cm]{geometry}
\usepackage{titling}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{doi}

\begin{document}

\centering{\large Biographical Sketch: Daniel S.\ Roche}

\begin{enumerate}[label=\textbf{(\alph*)}]

\item \textbf{Professional Preparation}
\begin{itemize}
  \item \textbf{Undergraduate Institution}: University of Delaware, Newark, DE, U.S.A\\
  B.S., Computer and Information Sciences, May 2006.\\
  B.S., Mathematical Sciences, May 2006.\\
  B.Mus., Applied Music Instrumental, Tuba, May 2006.

  \item \textbf{Graduate Institution}: University of Waterloo, Waterloo, Ontario, Canada\\
  Ph.D., Computer Science, June 2011.
\end{itemize}

\item \textbf{Appointments}
  \begin{itemize}
    \item United States Naval Academy, Computer Science Department.\\
      Associate Professor, 2016--present.\\
      Assistant Professor, 2011--2016.
  \end{itemize}

\item \textbf{Publications}

  \begin{enumerate}[label=(\roman*)]
    \item Closely related to proposed project
      \begin{enumerate}[label=\arabic*.]

        \item Daniel S.\ Roche, Daniel Apon, Seung Geol Choi,
          Arkady Yerukhimovich.\\
          ``POPE: Partial Order-Preserving Encoding''\\
          Proc. ACM Conf. on Computer and Communications Security (CCS) 2016.\\
          \url{https://arxiv.org/abs/1610.04025}

        \item Daniel S. Roche, Adam J. Aviv, Seung Geol Choi, Travis
          Mayberry.\\
          ``Deterministic, Stash-Free Write-Only ORAM''\\
          Proc. ACM Conf. on Computer and Communications Security (CCS) 2017.\\
          \url{https://arxiv.org/abs/1706.03827}

        \item Adam J. Aviv, Seung Geol Choi, Travis Mayberry, Daniel S.
        Roche.\\
          ``ObliviSync: Practical Oblivious File Backup and
          Synchronization''\\
          Network and Distributed System Security Symposium (NDSS)
          2017.\\
          \url{https://arxiv.org/abs/1605.09779}

        \item Daniel S. Roche, Adam J. Aviv, Seung Geol Choi.\\
          ``A Practical Oblivious Map Data Structure with Secure
          Deletion and History Independence''\\
          IEEE Symposium on Security and Privacy (S\&P) 2016.\\
          \url{https://arxiv.org/abs/1505.07391}

        \item Mohamed Khochtali, Daniel S.\ Roche, Xisen Tian.\\
          ``Parallel sparse interpolation using small primes.''\\
          Proc.\ 2015 International Workshop on Parallel Symbolic
          Computation (PASCO).\\
          \url{https://arxiv.org/abs/1506.04215}

      \end{enumerate}

    \item Other significant publications
      \begin{enumerate}[label=\arabic*.]
        \item Andrew Arnold and Daniel S.\ Roche.\\
          ``Output-sensitive algorithms for sumset and sparse polynomial
          multiplication.'' \\
          Proc.\ 40th ACM International Symposium on Symbolic and
          Algebraic Computation\\ (ACM ISSAC), 2015.
          \doi{10.1145/2755996.2756653}

        \item Andrew Arnold and Daniel S.\ Roche.\\
          ``Multivariate sparse interpolation using randomized Kronecker
          substitutions.'' \\
          Proc.\ 39th ACM ISSAC, 2014.
          \doi{10.1145/2608628.2608674}

        \item Daniel S. Roche. 
          ``Chunky and Equal-Spaced Polynomial Multiplication.''\\
          \textit{Journal of Symbolic Computation}, Vol.~46, Issue 7, Jul.~2011,
          pp.~791--806.\\
          \doi{10.1016/j.jsc.2010.08.013}

        \item Mark Giesbrecht and Daniel S. Roche.
          ``Detecting lacunary perfect powers and computing their roots.''
          \textit{Journal of Symbolic Computation}, Vol.~46, Issue 11, Nov.~2011,
          pp.\ 1242--1259.
          \doi{10.1016/j.jsc.2011.08.006}

        \item Mark Giesbrecht and Daniel S. Roche.
          ``Interpolation of Shifted-Lacunary Polynomials.''
          \textit{Computational Complexity}, Vol.~19 No.~3, 2010, pp.
          333--354. \\
          \doi{10.1007/s00037-010-0294-0}
      \end{enumerate}

  \end{enumerate}

\item \textbf{Synergistic Activities}
  \begin{enumerate}[label=\arabic*.]
    \item Steering committee chair for ACM International Symposium on
      Symbolic and Algebraic Computation (ISSAC), 2015--2018 (currently
      chair).
    \item Treasurer for ACM Special Interest Group on Symbolic and
      Algebraic Computation (SIGSAM), 2017--present.
    \item Completed 6 undergraduate research projects involving 10 students over
      the past five years.
    \item General chair of East Coast Computer Algebra Day (ECCAD) 2013, 
      held at the U.\ S.\ Naval Academy in April, 2013.
      This is an annual research conference with an emphasis on
      student contributions. The ``theme'' for this ECCAD was
      ``Connections between computer algebra and computer security.'' 
    \item Curriculum development: Developed a new undergraduate course at the
      Naval Academy on ``Randomness and Computation'', including topics
      on security protocols and cryptography.
      % This course exposes upper-level computer science students to new
      % algorithms and analysis techniques using randomization, including
      % cutting-edge research results in the area.
  \end{enumerate}

\end{enumerate}

\end{document}
